---
title: "Practical One"
author: ""
format: html
editor: visual
---

## Part 1:

Find all rows in “airquality” that have missing values.

```{r}
rows_with_na <- airquality[rowSums(is.na(airquality))>0, ]
as.integer(rownames(rows_with_na))
```

## Part 2:

Find mean, sd, min, max for each of temperature and ozone level.

### Temperature

```{r}
mean(airquality$Temp)
sd(airquality$Temp)
min(airquality$Temp)
max(airquality$Temp)
```

### Ozone 

```{r}
mean(airquality$Ozone, na.rm = TRUE)
sd(airquality$Ozone, na.rm = TRUE)
min(airquality$Ozone, na.rm = TRUE)
max(airquality$Ozone, na.rm = TRUE)
```

## Part 3:

The cars data contains two variables: speed and distance to stop. Fit a simple linear regression model to these data, i.e. find the estimates.

```{r}
x <- cbind(1, cars$speed)
y <- cars$dist

beta <- solve(t(x)%*%x)%*%t(x)%*%y
beta
```

## Part 4:

1.  Check that you get the same beta estimates as when fitting the linear regression model using lm() in R.

```{r}
model <- lm(dist ~ speed, data = cars)
summary(model)
```
